Adaptive group-regularized logistic elastic net regression

### 2019-02-20 docs/manuscript.Rnw
made start with micrornaseq_colorectal_cancer.R analysis

	\section*{Software}
	The method is available as an \texttt{R} package from \url{https://CRAN.R-project.org/package=gren}.

	\section*{Supplementary Material}
	Supplementary Material is available online from \url{http://pub.math.leidenuniv.nl/~munchmm/}.

>>>>

	\section*{Software}
	A (stable) \texttt{R} package is available from 
	\url{https://CRAN.R-project.org/package=gren}.

	\section*{Supplementary Material}
	Supplementary Material is available online from 
	\url{http://pub.math.leidenuniv.nl/~munchmm/}. All materials needed to   
	recreate this document are available from 
	\url{https://github.com/magnusmunch/gren}.
